A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-02-01 Article.qmd
-

```{r dependancies, cache = FALSE, include = FALSE}
library(ggplot2);   library(tidyverse);   library(gridExtra);   library(rjags);   library(paletteer);   
library(latex2exp);   library(grid);   library(dplyr);   library(tidyr);   library(tibble)

>>>>

```{r dependancies, cache = FALSE, include = FALSE}
library(ggplot2);   library(tidyverse);   library(gridExtra);   library(rjags);   
library(latex2exp);   library(grid);   library(dplyr);   library(tidyr);   library(tibble)
